Homework 5

### 2019-10-02 hw5/MSimonsHW5.tex
corrected HW 5 problem 2

\item Assume that if $f(x)$, $g(x)$, $s(x)$, $d(x)$, $p(x)$ in $S[x]$ satisfy
\[
f(x) + g(x) = s(x)
\] \[
f(x) - g(x) = d(x)
\] \[
f(x)g(x) = p(x)
\]
then
\[
\] \[
f(\alpha) + g(\alpha) = s(\alpha)
\] \[
f(\alpha) - g(\alpha) = d(\alpha)
\] \[
f(\alpha)g(\alpha) = p(\alpha)
\]
We can prove that $\phi_{\alpha}$ is closed under addition as such:
\[
\phi_{\alpha}(f) + \phi_{\alpha}(g) = f(\alpha) + g(\alpha) = s(\alpha) = \phi_{\alpha}(s)
\] \[
\phi_{\alpha}(f) - \phi_{\alpha}(g) = f(\alpha) - g(\alpha) = d(\alpha) = \phi_{\alpha}(d)
\]
We can prove that $\phi_{\alpha}$ is closed under multiplication as such:
\[
\phi_{\alpha}(f)\phi_{\alpha}(g) = f(\alpha)g(\alpha) = p(\alpha) = \phi_{\alpha}(p)
\]
Thus, $\phi_{\alpha}$ is a ring homomorphism.

\item Let $f(\alpha)$, $g(\alpha)$ be any elements in $S[\alpha]$.  By the
definition of $S[\alpha]$, $f(x)$, $g(x)$ as elements of $S[x]$.  Since $S[x]$
is a ring homomorphism, $(f+g)(x)$ is an element of $S[x]$.  If $(f+g)(x)$ is an
element of $S[x]$, then $(f+g)(\alpha)$ is an element of $S[\alpha]$ and
$S[\alpha]$ is closed under addition.
\\
\\
Similarly, $f(x)g(x)$ is an element of $S[x]$.  This implies that
$f(\alpha)g(\alpha)$ is an element of $S[\alpha]$ and so $S[\alpha]$ is
closed under multiplication.
\\
\\
For $S[\alpha]$ to be a subring of $R$, $0_R$ must be an element of $S[\alpha]$.
Define the function $f:S[x] \rightarrow R$ by $f(x) = 0_R$.  As such,
$f(\alpha) = 0_R$ is an element of $S[\alpha]$.
\\
\\
Let $f(x) = a_0 + a_{1}x + ... + a_{n}x^n$ be any element of $S[x]$.
By definition, $a_i$ is an element of $R$ for all non-negative integers $i$, and
for all $a_i$, there exists a $b_i$ in $R$ such that $a_i + b_i = 0_R$.
Therefore, there exists a function $g(x) = b_0 + b_{1}x + ... + b_{n}x^n$ in
$S[x]$ such that $f(x) + g(x) = 0_R$.  As a direct result, for any $f(\alpha)$
in $S[\alpha]$ there exists a $g(\alpha)$ such that
$f(\alpha) + g(\alpha) = 0_R$.
\\
\\
Thus, $S[\alpha]$ is a subring of $R$.

>>>>

\item Assume that if $f(x)$, $g(x)$, $s(x)$, $d(x)$, $p(x)$ in $S[x]$ satisfy
\[
f(x) + g(x) = s(x)
\] \[
f(x) - g(x) = d(x)
\] \[
f(x)g(x) = p(x)
\]
then, for any $\alpha$ in $R$,
\[
\] \[
f(\alpha) + g(\alpha) = s(\alpha)
\] \[
f(\alpha) - g(\alpha) = d(\alpha)
\] \[
f(\alpha)g(\alpha) = p(\alpha)
\]
We can prove that $\phi_{\alpha}$ is closed under addition as such:
\[
\phi_{\alpha}(f) + \phi_{\alpha}(g) = f(\alpha) + g(\alpha) = s(\alpha) = \phi_{\alpha}(s)
\] \[
\phi_{\alpha}(f) - \phi_{\alpha}(g) = f(\alpha) - g(\alpha) = d(\alpha) = \phi_{\alpha}(d)
\]
We can prove that $\phi_{\alpha}$ is closed under multiplication as such:
\[
\phi_{\alpha}(f)\phi_{\alpha}(g) = f(\alpha)g(\alpha) = p(\alpha) = \phi_{\alpha}(p)
\]
Thus, $\phi_{\alpha}$ is a ring homomorphism.

\item Let $f(\alpha)$, $g(\alpha)$ be elements in $S[\alpha]$.  This implies
that $f(x)$ and $g(x)$ are elements of $S[x]$.  Since $S$ is a ring, its
elements are closed under addition, implying that $S[x]$ is closed under
addition as well.  Let $f(x) + g(x) = s(x)$ and $f(x) - g(x) = d(x)$.  Since
$s(x)$ and $d(x)$ are in $S[x]$, $s(\alpha) = f(\alpha) + g(\alpha)$ and
$d(\alpha) = f(\alpha) - g(\alpha)$ are elements of $S[\alpha]$ and $S[\alpha]$
is closed under addition.
\\
\\
Similarly, since $S$ is closed under multiplication, we can assume $p(x) = f(x)g(x)$
is an element of $S[x]$.  Therefore $p(\alpha) = f(\alpha)g(\alpha)$ is an
element of $S[\alpha]$ and $S[alpha]$ is closed under multiplication.
\\
\\
Thus, $S[\alpha]$ is a subring of $R$.
